Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-12-29 manuscript.tex
preparando todo para scholar one

\author[Lares, Funes \& Gramajo]{Lares M$^{1, 2}$, Funes J.~G.$^{1, 3}$ \& Gramajo
L$^{1, 2}$}

@@

\selfcitation{Lares M, Funes J (XXXX).  Estimating the probability of
causal contact between civilizations through MonteCarlo simulations,
International Journal of Astrobiology}

@@

%%% S E C T I O N - - - - - - - - - - - - - - - - - - - - - - -
\input{motivations}

%%% S E C T I O N - - - - - - - - - - - - - - - - - - - - - - -
\input{methods}

%%% S E C T I O N - - - - - - - - - - - - - - - - - - - - - - -
\input{results}

@@

>>>>

\author[Lares, Funes \& Gramajo]{Lares M.$^{1, 2}$, Funes J.~G.$^{1,
3}$ \& Gramajo L.$^{1, 2}$}

@@

@@

%%% S E C T I O N - - - - - - - - - - - - - - - - - - - - - - -
\input{Sec_motivations}

%%% S E C T I O N - - - - - - - - - - - - - - - - - - - - - - -
\input{Sec_methods}

%%% S E C T I O N - - - - - - - - - - - - - - - - - - - - - - -
\input{Sec_results}

@@

\ack[Disclosure statement]{
%
No competing financial interests exist.
%
}
